

# Summary (dashboard)

## ... 


### Today{.value-box}

```{r}

#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"


# https://github.com/rstudio/flexdashboard/blob/main/inst/examples/crandash/crandash.Rmd

# downloadRate is a reactive expression that computes the download
# rate during this dashboard's lifetime.
startTime <- as.numeric(Sys.time())
downloadRate <- reactive({
  elapsed <- as.numeric(Sys.time()) - startTime
  
})
# Emit the download rate
renderValueBox({
  rate <- formatC(111111, digits = 1, format = "f")
  valueBox(
    value = rate,
    icon = "fa-area-chart",
    color =  "warning"
  )
})
```




### Total downloads {.value-box}

```{r}
# dlCount is a reactive expression that keeps track of the total
# number of rows that have ever appeared through pkgStream.

# Emit the download count
renderValueBox({
  valueBox(
    value = paste(format(1234567, big.mark = ","), "", sep = " "),
    caption = "Total confirmed cases",
    # icon = "fa-download",
    icon = "fas fa-heart-broken",
    # icon = "fas fa-user-md",
    color = "primary")
})
```

### Unique users {.value-box}

```{r}

renderValueBox({
  valueBox(value = 333.33, icon = "fa-users")
})
```




## ... Cases following vaccination {data-width=175}

<!-- Row {data-height=175} -->
<!-- ------------------------------------- -->



Cases following vaccination (Source: PHAC)


### Linked Value Box

```{r}
valueBox(42, icon = "fa-pencil", color = "yellow", href="#details")
# ("primary", "info", "success", "warning", "danger") 
```

renderValueBox({
rate <- formatC(downloadRate(), digits = 1, format = "f")
valueBox(
value = rate,
icon = "fa-area-chart",
color = if (rate >= input$rateThreshold) "warning" else "primary"
)
})

### Safety

```{r}
valueBox(2, icon="fa-hospital", caption="qwertyu")
```


## ... Side effects..... {data-width=175}

<!-- Row {data-height=175} -->
<!-- ------------------------------------- -->

Side effects following COVID-19 vaccination  (Source: PHAC)

### Linked Value Box

```{r}
valueBox(42, icon = "fa-pencil", color = "yellow", href="#details")
# ("primary", "info", "success", "warning", "danger") 
```

### C-19 naive 
```{r}
valueBox(2, icon="fa-hospital", caption="qwertyu")
```


### C-19 exposed 
```{r}
valueBox(2, icon="fa-tag" )
```


### C-19 vaccinated

```{r}
valueBox(2, icon="fa-tag" )
```


### C-19 cases
```{r}
valueBox(2, icon="fa-hospital")
```



### C-19 Hospitalizations
```{r}
valueBox(2, icon="fa-hospital")
```



### C-19 Deaths
```{r}
valueBox(2, icon="fa-tag" )
```




## ... Death  by causes ... {data-width=175}

<!-- Row {data-height=175} -->
<!-- ------------------------------------- -->


Deaths by causes (source; StatsCan) 

### Linked Value Box

```{r}
valueBox(42, icon = "fa-pencil", color = "yellow", href="#details")
# ("primary", "info", "success", "warning", "danger") 
```

### C-19 naive 
```{r}
valueBox(2, icon="fa-hospital", caption="qwertyu")
```


###  Regions with no C-19 mandates

```{r}
valueBox(7 , icon="fa-tag" )
# find more favicons here: https://fontawesome.com/icons?d=gallery
# https://ionic.io/ionicons

# https://getbootstrap.com/docs/5.1/components/accordion/

```


###  Regions with no masks

```{r}
valueBox(7 , icon="fa-tag" )

```


###  Regions declared C-19 pandemic over

```{r}
valueBox(7 , icon="fa-tag" )

```


### Severe C-19 vaccine events


```{r}
valueBox(7 , icon="fa-tag" )
```





## ... Death  by causes ... {data-width=175}

<!-- Row {data-height=175} -->
<!-- ------------------------------------- -->


Policy Stats (source; various) 



###  Regions declared C-19 pandemic over

```{r}
valueBox(7 , icon="fa-tag" )

```


### Severe C-19 vaccine events


```{r}
valueBox(7 , icon="fa-tag" )
```



## ..2nd .... {data-height=1000, .tabset}

### omg

```{r}



```

### it's taaabbbed

```{r}




```


## ..3nd .... 

### Fact Checker

✓
☑
✅

+	Plus Sign	&#43;	&#x002B;

&#f00c 



&#10036; &#10037; &#10038;

<FontAwesomeIcon icon="fa-solid fa-check" />



<i class="fa-solid fa-check">QWERTYUI</i>




### Fact Checker

✓

#### code from  coronavirus-dashboard

```{r}

# from coronavirus-dashboard
if (F) {
  
  library(dtplyr)
  # install.packages("devtools")
  # devtools::install_github("RamiKrispin/coronavirus", force = TRUE)
  library(coronavirus)
  data(coronavirus)
  coronavirus %>% setDT
  dfCanada <- coronavirus  [country == "Canada"]
  dfCanada$date %>% max  # "2021-10-13"
  
  df <- dfCanada %>% 
    #reactive({
    # coronavirus %>% lazy_dt() %>% 
    # dplyr::filter(date == max(date)) %>%
    #dplyr::filter(Country.Region == input$country) %>%
    dplyr::filter(country == "Canada") %>%
    dplyr::group_by(province, type) %>%
    dplyr::summarise(total = sum(cases)) %>%
    tidyr::pivot_wider(
      names_from = type,
      values_from = total
    ) %>%
    # dplyr::mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
    dplyr::mutate(unrecovered = confirmed - ifelse(is.na(death), 0, death)) %>%
    dplyr::arrange(-confirmed) %>%
    dplyr::ungroup() %>%
    # dplyr::mutate(country = dplyr::if_else(Country.Region == "United Arab Emirates", "UAE", Country.Region)) %>%
    # dplyr::mutate(country = dplyr::if_else(country == "Mainland China", "China", country)) %>%
    # dplyr::mutate(country = dplyr::if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
    dplyr::mutate(province = trimws(province)) %>%
    dplyr::mutate(province = factor(province, levels = province))
  
  #})
  
  df_daily <- 
    #reactive({
    coronavirus %>%
    #dplyr::filter(Country.Region == input$country) %>%
    dplyr::filter(Country.Region == "Canada") %>%
    dplyr::group_by(date, type) %>%
    dplyr::summarise(total = sum(cases, na.rm = TRUE)) %>%
    tidyr::pivot_wider(
      names_from = type,
      values_from = total
    ) %>%
    dplyr::arrange(date) %>%
    dplyr::ungroup() %>%
    #dplyr::mutate(active = confirmed - death - recovered) %>%
    dplyr::mutate(active = confirmed - death) %>%
    dplyr::mutate(
      confirmed_cum = cumsum(confirmed),
      death_cum = cumsum(death),
      # recovered_cum = cumsum(recovered),
      active_cum = cumsum(active)
    )
  # })
  
  df.today <- coronavirus %>% dplyr::filter(date == max(date)) # never used ??
  
  
  renderPrint({df %>% knitr::kable()
  })
  
  DT::renderDataTable({
    DT::datatable(    df, filter="top",      
                      options = list(bPaginate = T,      pageLength = 5
                      )  )
  })
  
  DT::renderDataTable({
    DT::datatable(    df_daily, filter="top",      
                      options = list(bPaginate = T,      pageLength = 5
                      )  )
  })
  
  DT::renderDataTable({
    DT::datatable(    df.today, filter="top",      
                      options = list(bPaginate = T,      pageLength = 5
                      )  )
  })
  
  
 renderText({
    cat(glue::glue("\n\n# {input$country} ({input$state}) on {input$date}\n\n"))
})

# renderText({
#   cat(paste0("\n\n# ", input$country), "\n\n")
# }) 
  
  
 # Plotting the data

daily_confirmed %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~date,
    y = ~Canada,
    type = "scatter",
    mode = "lines+markers",
    name = "Canada"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~France,
    type = "scatter",
    mode = "lines+markers",
    name = "France"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~Spain,
    type = "scatter",
    mode = "lines+markers",
    name = "Spain"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~Italy,
    type = "scatter",
    mode = "lines+markers",
    name = "Italy"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of new confirmed cases"),
    xaxis = list(title = "Date"),
    # paper_bgcolor = "black",
    # plot_bgcolor = "black",
    # font = list(color = 'white'),
    hovermode = "compare",
    margin = list(
      # l = 60,
      # r = 40,
      b = 10,
      t = 10,
      pad = 2
    )
  )
 
}

```
